Illusion Game Validation (Study 2)

### 2022-08-06 study2/study2.Rmd
Update study2.Rmd

```{r, echo = FALSE, warning=FALSE, message=FALSE}
options(digits = 3,
        mc.cores = 4,
        brms.algorithm = "sampling",
        brms.backend = "cmdstanr")

@@

# Transformation
df$Illusion_Difference_log <- log(1 + df$Illusion_Difference)
df$Illusion_Difference_sqrt <- sqrt(df$Illusion_Difference)
df$Illusion_Difference_cbrt <- round(df$Illusion_Difference**(1/3), 4)
df$Illusion_Strength_log <- sign(df$Illusion_Strength) * log(1 + abs(df$Illusion_Strength))
df$Illusion_Strength_sqrt <- sign(df$Illusion_Strength) * sqrt(abs(df$Illusion_Strength))
df$Illusion_Strength_cbrt <- sign(df$Illusion_Strength) * (abs(df$Illusion_Strength)**(1/3))

@@

```{r message=FALSE, warning=FALSE, fig.width=20, fig.height=20}
# RT distribution
p <- estimate_density(df, select = "RT", at = c("Participant", "Block")) |>
  group_by(Participant) |>
  normalize(select = "y") |>
  ungroup() |>
  mutate(color = ifelse(Participant %in% outliers, "red", "blue")) |>
  ggplot(aes(x = x, y = y)) +
  geom_area(data = normalize(estimate_density(df, select = "RT"), select = "y"), alpha = 0.2) +
  geom_line(aes(color = color, group = interaction(Participant, Block), linetype = Block)) +
  geom_vline(xintercept = 150, linetype = "dashed", color = "red") +
  scale_color_manual(values = c("red" = "red", "blue" = "blue"), guide = "none") +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  coord_cartesian(xlim = c(0, 3000)) +
  theme_modern() +
  theme(axis.text.y = element_blank()) +
  facet_wrap(~Participant) +
  labs(y = "", x = "Reaction Time (ms)")
# p
# ggsave("figures/outliers.png", p, width=20, height=15)

@@

```{r message=FALSE, warning=FALSE}
df <- df |> 
  group_by(Participant, Error) |> 
  mutate(Outlier = ifelse(Error == 0 & (RT < 150 | standardize(RT) > 4), TRUE, FALSE)) |> 
  ungroup()

p1 <- estimate_density(df, select = "RT", at = "Participant") |>
  group_by(Participant) |>
  normalize(select = "y") |>
  ungroup() |>
  merge(df |> 
    filter(Error == 0) |> 
    group_by(Participant) |> 
    summarize(Outlier = mean(RT) + 4 * sd(RT))) |> 
  mutate(Outlier = ifelse(x >= Outlier, TRUE, FALSE)) |> 
  ggplot(aes(x = x, y = y)) +
  geom_area(data = normalize(estimate_density(df, select = "RT"), select = "y"), alpha = 0.2) +
  geom_line(aes(color = Participant, linetype=Outlier)) +
  geom_vline(xintercept = c(150), linetype = "dashed", color = "red") +
  scale_color_material_d("rainbow", guide = "none") +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  guides(linetype = "none") +
  coord_cartesian(xlim = c(0, 4000)) +
  theme_modern() +
  theme(axis.text.y = element_blank()) +
  labs(y = "", x = "Reaction Time (ms)")

@@

We removed `r sum(df$Outlier)` (`r insight::format_value(sum(df$Outlier) / nrow(df), as_percent=TRUE)`) outlier trials (150 ms < RT < 4 SD above mean).

@@

  p1 <- data |>
    group_by(Illusion_Difference, Illusion_Strength, Answer) |>
    summarize(Error = mean(Error), .groups = "drop") |>
    ungroup() |>
    ggplot(aes(x = Illusion_Difference, y = Error)) +
    geom_bar(aes(fill = Illusion_Strength, group = Illusion_Strength), position = position_dodge(width = dodge1, preserve = "single"), stat = "identity", width=0.03) +
    # geom_line(aes(color = Illusion_Strength, group=Illusion_Strength), position = position_dodge(width=dodge1)) +
    geom_hline(yintercept = 0.5, linetype = "dotted", alpha = 0.3) +
    scale_y_continuous(limits = c(0, 1), expand = c(0, 0), labels = scales::percent) +
    scale_x_continuous(expand = c(0, 0)) +
    scale_fill_gradientn(colours = c("#4CAF50", "#009688", "#00BCD4", "#2196F3", "#3F51B5", "#673AB7", "#9C27B0")) +
    theme_modern() +
    labs(
      color = "Illusion Strength",
      fill = "Illusion Strength",
      y = "Probability of Error",
      x = "Task Difficulty"
    ) +
    theme(plot.title = element_text(face = "bold", hjust = 0.5))

  p2 <- data |>
    group_by(Illusion_Difference, Illusion_Strength, Answer) |>
    summarize(Error = mean(Error), .groups = "drop") |>
    ungroup() |>
    # mutate(Illusion_Difference = as.factor(round(Illusion_Difference, 4))) |>
    ggplot(aes(x = Illusion_Strength, y = Error)) +
    geom_hline(yintercept = 0.5, linetype = "dotted", alpha = 0.3) +
    geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.6) +
    geom_bar(aes(fill = Illusion_Difference, group = Illusion_Difference), position = position_dodge(width = dodge2, preserve = "single"), stat = "identity", width=0.1) +
    # geom_line(aes(color = Illusion_Difference), position = position_dodge(width=dodge2)) +
    scale_y_continuous(limits = c(0, 1), expand = c(0, 0), labels = scales::percent) +
    scale_x_continuous(expand = c(0, 0)) +
    scale_fill_gradientn(colours = c("#F44336", "#FFC107", "#4CAF50")) +
    theme_modern() +
    labs(
      color = "Task Difficulty",
      fill = "Task Difficulty",
      y = "Probability of Error",
      x = "Illusion Strength"
    ) +
    theme(plot.title = element_text(face = "bold", hjust = 0.5))

@@

  # Get predicted
  pred <- estimate_relation(model,
                            at = vars,
                            length = c(NA, 25))

@@

  # Manual jittering
  xrange <- 0.05*diff(range(data[[varstrength]]))
  data$x <- data[[varstrength]]
  data$x[data$x > 0] <- data$x[data$x > 0] - runif(sum(data$x > 0), 0, xrange)
  data$x[data$x < 0] <- data$x[data$x < 0] + runif(sum(data$x < 0), 0, xrange)
  data$x[round(data$x, 2) == 0] <- data$x[round(data$x, 2) == 0] + runif(sum(round(data$x, 2) == 0), -xrange/2, xrange/2)

  pred |>
    ggplot(aes_string(x = varstrength, y = "Predicted")) +
    geom_dots(
      data = data,
      aes(x=x, 
          y = Error, 
          group = Error,
          side = .dots_side, 
          # order=as.numeric(color) * ifelse(Error == 1, 1, -1)), 
          order=color), 
      fill = data$color,
      color = NA, 
      alpha=0.5) +
    geom_slab(data=data, aes(y = Error)) +
    geom_ribbon(aes_string(ymin = "CI_low", ymax = "CI_high", fill = vardiff, group = vardiff), alpha = 0.2) +
    geom_vline(xintercept = 0, linetype = "dashed") +
    geom_hline(yintercept = c(0.5), linetype = "dotted", alpha = 0.5) +
    geom_line(aes_string(color = vardiff, group = vardiff)) +
    scale_y_continuous(limits = c(0, 1), expand = c(0, 0), labels = scales::percent) +
    scale_x_continuous(expand = c(0, 0)) +
    scale_color_gradientn(colours = c("#F44336", "#FFC107", "#4CAF50")) +
    scale_fill_gradientn(colours = c("#F44336", "#FFC107", "#4CAF50")) +
    coord_cartesian(xlim=c(min(data[[varstrength]]), max(data[[varstrength]]))) +
    theme_modern() +
    labs(
      title = paste0(data$Illusion_Type[1], " Illusion"),
      color = "Difficulty", fill = "Difficulty",
      y = "Probability of Error",
      x = "Illusion Strength"
    ) +
    theme(plot.title = element_text(face = "bold", hjust = 0.5))
}

@@

```{r message=FALSE, warning=FALSE, cache=cache}
formula <- brms::bf(
  RT ~ Illusion_Difference * Illusion_Strength + 
    (1 + (Illusion_Difference * Illusion_Strength) | Participant),
  family="shifted_lognormal"
)

@@

modelbased::estimate_prediction(model_delboeuf_rt, keep_iterations = 10) |> 
  as.data.frame() |> 
  head()
  bayestestR::reshape_iterations()
nrow(as.data.frame(pred))
performance::check_model(model_delboeuf_rt)
# parameters::parameters(model)
```

@@

  p <- pred |>
    ggplot(aes_string(x = varstrength, y = "Predicted")) +
    ggdist::stat_slab(data=data, aes_string(y="RT", group = vardiff, fill=vardiff), alpha=0.5) +
    geom_ribbon(aes_string(ymin = "CI_low", ymax = "CI_high", fill = vardiff, group = vardiff), alpha = 0.2) +
    geom_vline(xintercept = 0, linetype = "dashed") +
    geom_line(aes_string(color = vardiff, group = vardiff)) +
    scale_y_continuous(expand = c(0, 0)) +
    scale_x_continuous(expand = c(0, 0)) +
    scale_color_gradientn(colours = c("#F44336", "#FFC107", "#4CAF50")) +
    scale_fill_gradientn(colours = c("#F44336", "#FFC107", "#4CAF50")) +
    coord_cartesian(xlim=c(min(data[[varstrength]]), max(data[[varstrength]])),
                    ylim=c(150, 2000)) +
    theme_modern() +
    labs(
      title = paste0(data$Illusion_Type[1], " Illusion"),
      color = "Difficulty", fill = "Difficulty",
      y = "Reaction Time (ms)",
      x = "Illusion Strength"
    ) +
    theme(plot.title = element_text(face = "bold", hjust = 0.5))

}

@@

```{r message=FALSE, warning=FALSE, cache=cache, fig.height=fig.height*2}
plot_all <- function(data, p_err, p_rt) {
  # Get stimuli
  dat <- df |>
    filter(Error == 0) |> 
    filter(Illusion_Type == unique(data$Illusion_Type),
           Answer %in% c("arrowleft", "arrowup")) |>
    select(Stimulus, Illusion_Strength, Illusion_Difference)

  dat <- rbind(
    filter(dat, Illusion_Strength == min(Illusion_Strength)) |> 
    filter(Illusion_Difference %in% c(min(Illusion_Difference), max(Illusion_Difference))),
    filter(dat, Illusion_Strength == max(Illusion_Strength)) |> 
    filter(Illusion_Difference %in% c(min(Illusion_Difference), max(Illusion_Difference))),
    filter(dat, Illusion_Difference == min(Illusion_Difference)) |> 
    filter(Illusion_Strength %in% c(min(Illusion_Strength), max(Illusion_Strength))),
    filter(dat, Illusion_Difference == max(Illusion_Difference)) |> 
    filter(Illusion_Strength %in% c(min(Illusion_Strength), max(Illusion_Strength))))

@@

  img_leftdown <- paste0("study2/stimuli/", img_leftdown, ".png") |> 
    png::readPNG() |> 
    grid::rasterGrob(interpolate=TRUE) |> 
    patchwork::wrap_elements()
  img_rightdown <- paste0("study2/stimuli/", img_rightdown, ".png") |> 
    png::readPNG() |> 
    grid::rasterGrob(interpolate=TRUE) |> 
    patchwork::wrap_elements()
  img_leftup <- paste0("study2/stimuli/", img_leftup, ".png") |> 
    png::readPNG() |>  
    grid::rasterGrob(interpolate=TRUE) |> 
    patchwork::wrap_elements()
  img_rightup <- paste0("study2/stimuli/", img_rightup, ".png") |> 
    png::readPNG() |> 
    grid::rasterGrob(interpolate=TRUE) |> 
    patchwork::wrap_elements()

  p <- ((p_err + labs(x = "")) / (p_rt + labs(title = "")) + patchwork::plot_layout(guides="collect"))

@@

```{r message=FALSE, warning=FALSE, cache=cache}
random <- model_delboeuf_err 
random <- as.data.frame(model_delboeuf_err)
random <- random[str_detect(names(random), "Participant\\[")]
random <- random |> 
  mutate(Draw = 1:nrow(random)) |>
  pivot_longer(-Draw, names_to="Parameter", values_to = "Value") |> 
  separate(Parameter, into = c("Participant", "Parameter"), sep = ",") |> 
  mutate(Participant = str_remove(Participant, "r_Participant\\["),
         Parameter = str_remove(Parameter, "]"))

random |> 
  ggplot(aes(y= Participant, x = Value)) +
  ggdist::stat_slabinterval() +
  facet_wrap(~Parameter)

data <- random |> 
  mutate(Parameter = paste0("Delboeuf_", Parameter)) |> 
  group_by(Participant, Parameter) |> 
  summarize(Score = as.numeric(bayestestR::map_estimate(Value)), .groups="drop") |>
  ungroup() |> 
  pivot_wider(names_from = Parameter, values_from = Score)

```

@@

```{r message=FALSE, warning=FALSE, cache=cache}
dat <- data.frame()
for(participant in unique(data$Participant)) {
  freq <- glm(Error ~ Illusion_Difference * Illusion_Strength, 
              family = "binomial",
              data=filter(df, Participant == participant, 
                          Illusion_Type == "Delboeuf"))

  parameters::parameters(freq)[1:2] |> 
    as.data.frame() |> 
    mutate(Participant = participant, 
           Parameter = paste0("freq_Delboeuf_", Parameter))
}
```

@@

## Variability

>>>>

```{r, echo = FALSE, warning=FALSE, message=FALSE}
options(
  digits = 3,
  mc.cores = 4,
  brms.algorithm = "sampling",
  brms.backend = "cmdstanr"
)

@@

# Transformation
df$Illusion_Difference_log <- log(1 + df$Illusion_Difference)
df$Illusion_Difference_sqrt <- sqrt(df$Illusion_Difference)
df$Illusion_Difference_cbrt <- round(df$Illusion_Difference**(1 / 3), 4)
df$Illusion_Strength_log <- sign(df$Illusion_Strength) * log(1 + abs(df$Illusion_Strength))
df$Illusion_Strength_sqrt <- sign(df$Illusion_Strength) * sqrt(abs(df$Illusion_Strength))
df$Illusion_Strength_cbrt <- sign(df$Illusion_Strength) * (abs(df$Illusion_Strength)**(1 / 3))

@@

```{r message=FALSE, warning=FALSE, fig.width=20, fig.height=20}
# RT distribution
p <- estimate_density(df, select = "RT", at = c("Participant", "Block")) |>
  group_by(Participant) |>
  normalize(select = "y") |>
  ungroup() |>
  mutate(color = ifelse(Participant %in% outliers, "red", "blue")) |>
  ggplot(aes(x = x, y = y)) +
  geom_area(data = normalize(estimate_density(df, select = "RT"), select = "y"), alpha = 0.2) +
  geom_line(aes(color = color, group = interaction(Participant, Block), linetype = Block)) +
  geom_vline(xintercept = 125, linetype = "dashed", color = "red") +
  scale_color_manual(values = c("red" = "red", "blue" = "blue"), guide = "none") +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  coord_cartesian(xlim = c(0, 3000)) +
  theme_modern() +
  theme(axis.text.y = element_blank()) +
  facet_wrap(~Participant) +
  labs(y = "", x = "Reaction Time (ms)")
# p
# ggsave("figures/outliers.png", p, width=20, height=15)

@@

```{r message=FALSE, warning=FALSE}
df <- df |>
  group_by(Participant, Error) |>
  mutate(Outlier = ifelse(Error == 0 & (RT < 125 | standardize(RT) > 4), TRUE, FALSE)) |>
  ungroup()

p1 <- estimate_density(df, select = "RT", at = "Participant") |>
  group_by(Participant) |>
  normalize(select = "y") |>
  ungroup() |>
  merge(df |>
    filter(Error == 0) |>
    group_by(Participant) |>
    summarize(Outlier = mean(RT) + 4 * sd(RT))) |>
  mutate(Outlier = ifelse(x >= Outlier, TRUE, FALSE)) |>
  ggplot(aes(x = x, y = y)) +
  geom_area(data = normalize(estimate_density(df, select = "RT"), select = "y"), alpha = 0.2) +
  geom_line(aes(color = Participant, linetype = Outlier)) +
  geom_vline(xintercept = c(125), linetype = "dashed", color = "red") +
  scale_color_material_d("rainbow", guide = "none") +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  guides(linetype = "none") +
  coord_cartesian(xlim = c(0, 4000)) +
  theme_modern() +
  theme(axis.text.y = element_blank()) +
  labs(y = "", x = "Reaction Time (ms)")

@@

We removed `r sum(df$Outlier)` (`r insight::format_value(sum(df$Outlier) / nrow(df), as_percent=TRUE)`) outlier trials (125 ms < RT < 4 SD above mean).

@@

  p1 <- data |>
    group_by(Illusion_Difference, Illusion_Strength, Answer) |>
    summarize(Error = mean(Error), .groups = "drop") |>
    ungroup() |>
    ggplot(aes(x = Illusion_Difference, y = Error)) +
    geom_bar(aes(fill = Illusion_Strength, group = Illusion_Strength), position = position_dodge(width = dodge1, preserve = "single"), stat = "identity", width = 0.03) +
    # geom_line(aes(color = Illusion_Strength, group=Illusion_Strength), position = position_dodge(width=dodge1)) +
    geom_hline(yintercept = 0.5, linetype = "dotted", alpha = 0.3) +
    scale_y_continuous(limits = c(0, 1), expand = c(0, 0), labels = scales::percent) +
    scale_x_continuous(expand = c(0, 0)) +
    scale_fill_gradientn(colours = c("#4CAF50", "#009688", "#00BCD4", "#2196F3", "#3F51B5", "#673AB7", "#9C27B0")) +
    theme_modern() +
    labs(
      color = "Illusion Strength",
      fill = "Illusion Strength",
      y = "Probability of Error",
      x = "Task Difficulty"
    ) +
    theme(plot.title = element_text(face = "bold", hjust = 0.5))

  p2 <- data |>
    group_by(Illusion_Difference, Illusion_Strength, Answer) |>
    summarize(Error = mean(Error), .groups = "drop") |>
    ungroup() |>
    # mutate(Illusion_Difference = as.factor(round(Illusion_Difference, 4))) |>
    ggplot(aes(x = Illusion_Strength, y = Error)) +
    geom_hline(yintercept = 0.5, linetype = "dotted", alpha = 0.3) +
    geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.6) +
    geom_bar(aes(fill = Illusion_Difference, group = Illusion_Difference), position = position_dodge(width = dodge2, preserve = "single"), stat = "identity", width = 0.1) +
    # geom_line(aes(color = Illusion_Difference), position = position_dodge(width=dodge2)) +
    scale_y_continuous(limits = c(0, 1), expand = c(0, 0), labels = scales::percent) +
    scale_x_continuous(expand = c(0, 0)) +
    scale_fill_gradientn(colours = c("#F44336", "#FFC107", "#4CAF50")) +
    theme_modern() +
    labs(
      color = "Task Difficulty",
      fill = "Task Difficulty",
      y = "Probability of Error",
      x = "Illusion Strength"
    ) +
    theme(plot.title = element_text(face = "bold", hjust = 0.5))

@@

  # Get predicted
  pred <- estimate_relation(model,
    at = vars,
    length = c(NA, 25)
  )

@@

  # Manual jittering
  xrange <- 0.05 * diff(range(data[[varstrength]]))
  data$x <- data[[varstrength]]
  data$x[data$x > 0] <- data$x[data$x > 0] - runif(sum(data$x > 0), 0, xrange)
  data$x[data$x < 0] <- data$x[data$x < 0] + runif(sum(data$x < 0), 0, xrange)
  data$x[round(data$x, 2) == 0] <- data$x[round(data$x, 2) == 0] + runif(sum(round(data$x, 2) == 0), -xrange / 2, xrange / 2)

  pred |>
    ggplot(aes_string(x = varstrength, y = "Predicted")) +
    geom_dots(
      data = data,
      aes(
        x = x,
        y = Error,
        group = Error,
        side = .dots_side,
        # order=as.numeric(color) * ifelse(Error == 1, 1, -1)),
        order = color
      ),
      fill = data$color,
      color = NA,
      alpha = 0.5
    ) +
    geom_slab(data = data, aes(y = Error)) +
    geom_ribbon(aes_string(ymin = "CI_low", ymax = "CI_high", fill = vardiff, group = vardiff), alpha = 0.2) +
    geom_vline(xintercept = 0, linetype = "dashed") +
    geom_hline(yintercept = c(0.5), linetype = "dotted", alpha = 0.5) +
    geom_line(aes_string(color = vardiff, group = vardiff)) +
    scale_y_continuous(limits = c(0, 1), expand = c(0, 0), labels = scales::percent) +
    scale_x_continuous(expand = c(0, 0)) +
    scale_color_gradientn(colours = c("#F44336", "#FFC107", "#4CAF50")) +
    scale_fill_gradientn(colours = c("#F44336", "#FFC107", "#4CAF50")) +
    coord_cartesian(xlim = c(min(data[[varstrength]]), max(data[[varstrength]]))) +
    theme_modern() +
    labs(
      title = paste0(data$Illusion_Type[1], " Illusion"),
      color = "Difficulty", fill = "Difficulty",
      y = "Probability of Error",
      x = "Illusion Strength"
    ) +
    theme(plot.title = element_text(face = "bold", hjust = 0.5))
}

@@

```{r message=FALSE, warning=FALSE, cache=cache}
formula <- brms::bf(
  RT ~ Illusion_Difference * Illusion_Strength +
    (1 + (Illusion_Difference * Illusion_Strength) | G | Participant),
  sigma ~ Illusion_Difference * Illusion_Strength +
    (1 + (Illusion_Difference * Illusion_Strength) | G | Participant),
  family = "shifted_lognormal"
)

@@

plot_ppcheck <- function(model) {
  pred <- modelbased::estimate_prediction(model_delboeuf_rt, keep_iterations = 100)
  estimate_density(pred$RT) |>
    ggplot(aes(x = x, y = y)) +
    geom_area(fill = "#9E9E9E") +
    geom_line(
      data = pred |>
        bayestestR::reshape_iterations() |>
        mutate(iter_group = as.factor(iter_group)) |>
        estimate_density(select = "iter_value", at = "iter_group"),
      aes(group = iter_group), color = "#2196F3", size = 0.1, alpha = 0.5
    ) +
    scale_y_continuous(expand = c(0, 0)) +
    scale_x_continuous(expand = c(0, 0)) +
    coord_cartesian(xlim = c(100, 3000)) +
    theme_modern() +
    labs(x = "Reaction Time (ms)", y = "", title = "Posterior Predictive Check") +
    theme(
      plot.title = element_text(face = "bold", hjust = 0.5),
      axis.text.y = element_blank()
    )
}

plot_ppcheck(model_delboeuf_rt)
# performance::check_model(model_delboeuf_rt)
# parameters::parameters(model)
```

@@

  p <- pred |>
    ggplot(aes_string(x = varstrength, y = "Predicted")) +
    ggdist::stat_slab(data = data, aes_string(y = "RT", group = vardiff, fill = vardiff), alpha = 0.5) +
    geom_ribbon(aes_string(ymin = "CI_low", ymax = "CI_high", fill = vardiff, group = vardiff), alpha = 0.2) +
    geom_vline(xintercept = 0, linetype = "dashed") +
    geom_line(aes_string(color = vardiff, group = vardiff)) +
    scale_y_continuous(expand = c(0, 0)) +
    scale_x_continuous(expand = c(0, 0)) +
    scale_color_gradientn(colours = c("#F44336", "#FFC107", "#4CAF50")) +
    scale_fill_gradientn(colours = c("#F44336", "#FFC107", "#4CAF50")) +
    coord_cartesian(
      xlim = c(min(data[[varstrength]]), max(data[[varstrength]])),
      ylim = c(125, 2000)
    ) +
    theme_modern() +
    labs(
      title = paste0(data$Illusion_Type[1], " Illusion"),
      color = "Difficulty", fill = "Difficulty",
      y = "Reaction Time (ms)",
      x = "Illusion Strength"
    ) +
    theme(plot.title = element_text(face = "bold", hjust = 0.5))
}

@@

```{r message=FALSE, warning=FALSE, cache=cache, fig.height=fig.height*2}
plot_all <- function(data, p_err, p_rt) {
  # Get stimuli
  dat <- df |>
    filter(Error == 0) |>
    filter(
      Illusion_Type == unique(data$Illusion_Type),
      Answer %in% c("arrowleft", "arrowup")
    ) |>
    select(Stimulus, Illusion_Strength, Illusion_Difference)

  dat <- rbind(
    filter(dat, Illusion_Strength == min(Illusion_Strength)) |>
      filter(Illusion_Difference %in% c(min(Illusion_Difference), max(Illusion_Difference))),
    filter(dat, Illusion_Strength == max(Illusion_Strength)) |>
      filter(Illusion_Difference %in% c(min(Illusion_Difference), max(Illusion_Difference))),
    filter(dat, Illusion_Difference == min(Illusion_Difference)) |>
      filter(Illusion_Strength %in% c(min(Illusion_Strength), max(Illusion_Strength))),
    filter(dat, Illusion_Difference == max(Illusion_Difference)) |>
      filter(Illusion_Strength %in% c(min(Illusion_Strength), max(Illusion_Strength)))
  )

@@

  img_leftdown <- paste0("stimuli/", img_leftdown, ".png") |>
    png::readPNG() |>
    grid::rasterGrob(interpolate = TRUE) |>
    patchwork::wrap_elements()
  img_rightdown <- paste0("stimuli/", img_rightdown, ".png") |>
    png::readPNG() |>
    grid::rasterGrob(interpolate = TRUE) |>
    patchwork::wrap_elements()
  img_leftup <- paste0("stimuli/", img_leftup, ".png") |>
    png::readPNG() |>
    grid::rasterGrob(interpolate = TRUE) |>
    patchwork::wrap_elements()
  img_rightup <- paste0("stimuli/", img_rightup, ".png") |>
    png::readPNG() |>
    grid::rasterGrob(interpolate = TRUE) |>
    patchwork::wrap_elements()

  p <- ((p_err + labs(x = "")) / (p_rt + labs(title = "")) + patchwork::plot_layout(guides = "collect"))

@@

```{r message=FALSE, warning=FALSE, cache=cache}
extract_random <- function(model, illusion = "Delboeuf") {
  random <- as.data.frame(model_delboeuf_rt)
  random <- random[str_detect(names(random), regex("^r_Participant"))]

  if (insight::model_info(model)$is_logit) {
    param <- "Prob,"
  } else {
    param <- "Loc,"
  }

  random |>
    mutate(Draw = 1:nrow(random)) |>
    pivot_longer(-Draw, names_to = "Parameter", values_to = "Value") |>
    mutate(
      Parameter = str_remove(Parameter, "r_Participant"),
      Parameter = str_remove(Parameter, "\\]"),
      Parameter = str_remove(Parameter, "\\["),
      Parameter = paste0(param, Parameter),
      Parameter = str_replace(Parameter, paste0(param, "__sigma"), "Disp,")
    ) |>
    separate(Parameter, into = c("Component", "Participant", "Parameter"), sep = ",") |>
    mutate(
      Parameter = paste0(Parameter, "_", Component),
      Illusion_Type = illusion
    ) |>
    mutate(
      Parameter = str_replace(Parameter, "Illusion_Strength", "Illu"),
      Parameter = str_replace(Parameter, "Illusion_Difference", "Diff")
    )
}

random <- rbind(
  extract_random(model_delboeuf_rt, "Delboeuf"),
  extract_random(model_delboeuf_err, "Delboeuf")
)

random |>
  ggplot(aes(y = Participant, x = Value)) +
  ggdist::stat_slabinterval(aes(fill = Illusion_Type)) +
  facet_wrap(~Parameter, scales = "free_x")

random <- random |>
  mutate(Parameter = paste0(Illusion_Type, "_", Parameter)) |>
  group_by(Participant, Parameter) |>
  summarize(Score = as.numeric(bayestestR::map_estimate(Value)), .groups = "drop") |>
  ungroup() |>
  pivot_wider(names_from = Parameter, values_from = Score)
```

@@

```{r message=FALSE, warning=FALSE, cache=cache}
dat <- data.frame()
for (participant in unique(data$Participant)) {
  freq <- glm(Error ~ Illusion_Difference * Illusion_Strength,
    family = "binomial",
    data = filter(
      df, Participant == participant,
      Illusion_Type == "Delboeuf"
    )
  )

  parameters::parameters(freq)[1:2] |>
    as.data.frame() |>
    mutate(
      Participant = participant,
      Parameter = paste0("freq_Delboeuf_", Parameter)
    )
}
```

@@

### Correlation

```{r message=FALSE, warning=FALSE, cache=cache}
clean_name <- function(x) {
  x |>
    str_replace("_Loc", " (loc)") |>
    str_replace("_Disp", " (disp)") |>
    str_replace("_Prob", " (prob)") |>
    str_replace("_", " - ")
}

cor <- correlation::correlation(random, redundant = TRUE)

p_data <- cor |>
  mutate(
    Parameter1 = clean_name(Parameter1),
    Parameter2 = clean_name(Parameter2)
  ) |>
  correlation::cor_sort(hclust_method = "ward.D2") |>
  cor_lower() |>
  mutate(
    Text = insight::format_value(r, zap_small = TRUE, digits = 3),
    Text = str_replace(str_remove(Text, "^0+"), "^-0+", "-"),
    Parameter2 = fct_rev(Parameter2)
  )

p_data |>
  ggplot(aes(x = Parameter2, y = Parameter1)) +
  geom_tile(aes(fill = r)) +
  # geom_text(aes(label = Text), size = 2) +
  scale_fill_gradient2(low = "#2196F3", mid = "white", high = "#F44336", midpoint = 0, limit = c(-1, 1), space = "Lab", name = "Correlation", guide = "legend") +
  scale_x_discrete(expand = c(0, 0)) +
  scale_y_discrete(expand = c(0, 0)) +
  labs(title = "Correlation Matrix", x = NULL, y = NULL) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 90, hjust = 1),
    plot.title = element_text(hjust = 0.5, face = "bold"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank()
  )
```

### Factor Analysis

#### First Level

```{r message=FALSE, warning=FALSE, cache=cache}
data <- select(random, -Participant)

rez <- parameters::n_factors(data)
plot(rez)

fa <- parameters::factor_analysis(data,
  cor = as.matrix(cor),
  n = 3,
  rotation = "oblimin",
  sort = TRUE
)

# psych::omega(data, nfactors=3)
# fa <- psych::fa.multi(as.matrix(cor), nfactors = 3, nfact2 = 1, n.obs = nrow(random))
# psych::fa.multi.diagram(fa)
```

#### Second Level

```{r message=FALSE, warning=FALSE, cache=cache}
data <- predict(fa)

rez <- parameters::n_factors(data, rotation = "oblimin")
plot(rez)

fa2 <- parameters::factor_analysis(data,
  n = 1,
  sort = TRUE
)

# psych::schmid(attributes(fa)$model, nfactors = 1)
```

#### Visualization
```{r message=FALSE, warning=FALSE, cache=cache}
library(ggraph)

dat <- rbind(
  attributes(fa)$loadings_long,
  attributes(fa2)$loadings_long |>
    mutate(Component = str_replace(Component, "MR1", "G"))
) |>
  tidygraph::as_tbl_graph() |>
  tidygraph::activate("nodes")

# Get order of indices
idx <- correlation::cor_sort(cor, hclust_method = "ward.D2") |>
  summary() |>
  pull(Parameter)

dat |>
  mutate(
    x = sapply(as.data.frame(dat)$name, function(x) {
      if (x %in% idx) {
        (which(idx == x) - 1) / (length(idx) - 1)
      } else {
        NA
      }
    })
  ) |>
  mutate(
    x = case_when(
    name == "G" ~ 0.5,
    name == "MR1" ~ 0,
    name == "MR2" ~ 0.5,
    name == "MR3" ~ 1,
    TRUE ~ x),
    y = case_when(
    name == "G" ~ 2,
    name == "MR1" ~ 1,
    name == "MR2" ~ 1,
    name == "MR3" ~ 1,
    TRUE ~ 0)) |> 
  ggraph(layout = "nicely") +
  geom_edge_link(aes(edge_width = Loading, edge_colour = as.factor(sign(Loading)))) +
  geom_node_point() +
  geom_node_text(aes(label = name)) +
  guides(edge_colour = "none") +
  ggraph::theme_graph()
```

```{r message=FALSE, warning=FALSE, cache=cache}
# Save
dfsub <- dfsub |> 
  merge(random, by = "Participant") |> 
  cbind(data, predict(fa2, names="G"))

write.csv("../data/study3.csv")
```
